An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-29 Revision/response.tex

\begin{figure}[htbp]
	\centering
	\includegraphics[width=\linewidth]{fig/exp_5_2_1.pdf}
	\caption{}
	\label{fig:attribute_selectivity}
\end{figure}

\textcolor{blue}{"The proximity of the 4 curves in the figure reflects algorithm sensitivity to distributional variations. When the curves converge closely, the algorithm demonstrates strong resilience against attribute distribution shifts."}

%%%%%%%%%%%%%%%%%%%%%% R2 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run experiments with multi-modal queries (e.g., combining text and images) or more complex query types involving both attribute and range filters.}
	\end{metarevision}
}

\noindent
\textbf{Response:} We believe this is an excellent suggestion. In fact, in the initial version of our paper, we used the text-to-image dataset that has been widely adopted by existing multimodal ANN algorithms. In this dataset, the base vectors are images, while the query set consists of texts, resulting in a modality gap between the two. Achieving good performance on such a dataset often requires the algorithm to demonstrate stronger robustness. \textbf{(Please see Section 4.2.3 and Section 4.3.3, highlighted in green in the revised manuscript.)}

@@

To further enrich the evaluation of complex multimodal queries, we have added new experiments in the Multi-modal Queries sections of Section 4.2.4 and Section 4.3.4. Specifically, we constructed a more challenging multimodal dataset by selecting 500,000 text vectors and 500,000 image vectors as the base set, and 5,000 text vectors and 5,000 image vectors as the query set. We then perform both attribute filtering and range queries over this dataset, combining text and image queries to further analyze the robustness of the algorithms. The corresponding experimental results are presented in Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.

As for complex query types that involve both attribute filtering and range queries simultaneously, to the best of our knowledge, existing algorithms—except for general-purpose systems such as Milvus and Faiss—do not support this functionality. For example, ACORN needs to build separate indexes for each scenario and cannot handle attribute filtering and range queries simultaneously. Therefore, we do not consider this type of complex query in our experiments but instead study the two query types separately. \textbf{(Please see Section 4.1.1, Section 4.2.4 and Secntion 4.3.4, highlighted in blue in the revised manuscript.)  
	%Please refer to the blue highlighted parts in  Section 4.1.1 paragraph 4 and  Section 4.2.4 and Section 4.3.4 under Multi-modal Queries.)
}

Section 4.1.1:\textcolor{blue}{
"Additionally, we use the Out-of-Distribution (OOD) dataset Text2Image and the large-scale dataset Deep100M to evaluate the generalization capability of the algorithms. The Text2Image dataset includes two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings."
}

Section 4.2.4: \textcolor{blue}{
	"We conducted experiments on the text2image-mix dataset. This dataset contains both image and text vectors. It is a more complex multimodal dataset. As shown in Figure 12, although the queries are more complex, UNG and NHQ still perform the best. CAPS is the next best.
	Since the dataset mixes two modalities, the ground truth of the query set usually corresponds to the same modality. The nearest neighbors in the index are often from the same modality because they are closer in distance. Therefore, the search results on this dataset are similar to those in Figure 4. UNG and NHQ perform the best. CAPS clusters based on vector similarity. It actually clusters the vectors into the same modality. Then it uses attribute filtering to divide the data further. This allows CAPS to quickly find nearest neighbors that meet the filter conditions.
	In contrast, the text2image dataset shown in Figure 11 is different. The queries and the dataset are from different modalities. The queries are far from the dataset. The ground truths are also scattered and not clustered together. To find the ground truths, the algorithm often needs to traverse more points. This is a greater challenge for the algorithms." 
}

Section 4.3.4:\textcolor{blue}{
		"Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure 16a is also consistent with the single-modality results in Figure 14. As shown in Figure 15, the algorithms still perform the worst on multimodal datasets like Text2Image. This is because these range query algorithms are almost graph-based. Graph algorithms need more iterations to find true neighbors in OOD datasets."
}

### 2025-07-29 VLDB2026/main.tex
Update main.tex

		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
		\caption{Hybrid query example}

@@

		\caption{Graph index and IVF index}

@@

		\caption{\textcolor{orange}{Comparison of AF-ANN and RF-ANN search algorithms}}
		\small
%		\label{tab:compair_1}
%		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
%			\hline
%			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
%			\hline
%			NHQ & Graph & C & Y & N& N& N & N & N \\
%			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
%			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
%			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
%			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
%			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
%			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
%			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
%			
%			\hline
%			
%		\end{tabular}
	\label{tab:compair_1}
	\begin{tabular}{|l|l|*{12}{c|}}
		\hline

@@

			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
			\caption{Construction time}
			\label{fig:build_time_comparison_query1}
		\end{subfigure}

@@

			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
			\caption{Index size (including original dataset)}
			\label{fig:index_size_mb_comparison_query1}
		\end{subfigure}

@@

			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Build peak memory }
			\label{fig:build_memory_mb_comparison}
		\end{subfigure}

@@

			\includegraphics[width=0.99\linewidth]{figures/searchMem/label_memory_comparison.pdf}
			\caption{Search peak memory}
			\label{fig:search_memory_mb_comparison}
		\end{subfigure}

		%		\caption{Time and space overhead of attribute filtering index construction}
		\caption{\textcolor{violet}{Time and space overhead}}
		\label{fig:build_index_comparison}
	\end{figure}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Single-Attribute Building and Query performance (single thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
		\caption{Single-Attribute Building and Query performance (16 threads)}
		\label{fig:exp_1_2_SingleLabel_16thread}
	\end{figure*}

@@

	\textit{\textbf{Single-Attribute Building and Single-Attribute Query.}}
	In this scenario, we construct the index using an attribute and apply filtering conditions on the same attribute.

@@

	\textit{\textbf{Multi-Attribute Building and Single-Attribute Query.}}
	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query.

@@

		% 下面的子图，居中显示
		\includegraphics[width=0.7\columnwidth]{figures/exp/exp_2_1.pdf}
		\caption{Effect of Multi-Attribute Index Construction on Single Query Performance. ($S$ denotes single-attribute index construction and single-attribute query; $M$ denotes multi-attribute index construction and single-attribute query)}
		\label{fig:exp_2_1}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
		\caption{Multi-attribute build and query performance (single thread)}
		\label{fig:exp_4_1_MultiLabel_1thread}
	\end{figure*}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}

		\footnotesize{
		\begin{center}
			\begin{minipage}{\linewidth}
				\centering	
				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
			\end{minipage}
		\end{center}
		}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{violet}{In this experiment, we only evaluate algorithms that support this multi-attribute query scenario.}

@@

			\includegraphics[width=0.95\textwidth]{figures/exp/exp_5_2_1.pdf}
			\caption{Algorithms optimized for low AS.}
			\label{fig:exp_5_2_1}
		\end{subfigure}

@@

			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_2.pdf}
			\caption{Algorithms optimized for high AS.}
			\label{fig:exp_5_2_2}
		\end{subfigure}
		\hspace{1mm} % 增加水平间距
		\begin{subfigure}{0.33\textwidth} % 1/3 宽度
			\centering

			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_3.pdf}
			\caption{Algorithms insensitive to AS.}
			\label{fig:exp_5_2_3}
		\end{subfigure}

		\caption{Different AS under the same algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

	\begin{figure*}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
		\caption{Effect of dataset on Query}
		\label{fig:exp_6_1}
	\end{figure*}

@@

	% 2. 第一部分：两张图，共用标题
	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
	% 宽度从\textwidth缩小到0.32\textwidth
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
		\caption{MultiModal}
		\label{fig:attribute-multimodal} 
	\end{subfigure}
	\hfill % 在第一部分和第二部分之间添加弹性间距
	% 3. 第二部分：两张图，共用标题
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
		\caption{Cross-Platform}
		\label{fig:attribute-cross-platform}
	\end{subfigure}
	\hfill % 在第二部分和第三部分之间添加弹性间距
	% 4. 第三部分：只有一张图
	\begin{subfigure}[b]{0.203\textwidth}
		\centering
		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
		\caption{Big Dataset}
		\label{fig:attribute big dataset}
	\end{subfigure}

	% 5. 全局总标题
	\caption{\textcolor{violet}Scalability Study——Attribution}
	\label{fig:TrinityExtension——Attribution_main}
\end{figure*}

@@

\textit{\textbf{\textcolor{blue}{Multi-modal Queries}}}

\textcolor{blue}{

@@

		% 三图横排
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{\footnotesize Construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{\footnotesize Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{\footnotesize Build peak memory}
			\label{fig:rangeFilter_build_memory_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
			\caption{\footnotesize Search peak memory}
			\label{fig:rangeFilter_search_memory_mb}
		\end{subfigure}

		%		\caption{Time and space overhead of range filtering index construction}
%		\caption{Time and space overhead of index construction}
		\caption{\textcolor{violet}{Time and space overhead}}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}
	\subsection{Range Filtering}
	\textcolor{blue}{Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value. The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones. }
	\subsubsection{Time and Space overhead of index construction.}

@@

		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
		\caption{RF-ANN search performance }
		\label{fig:exp_8_2}
	\end{figure*}

@@

	\begin{figure*}[htbp]
		\centering
		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

@@

	% 2. 第一部分：两张图，共用标题
	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
	% 宽度从\textwidth缩小到0.32\textwidth
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
		\caption{MultiModal}
		\label{fig:range-multimodal} 
	\end{subfigure}
	\hfill % 在第一部分和第二部分之间添加弹性间距
	% 3. 第二部分：两张图，共用标题
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
		\caption{Cross-Platform}
		\label{fig:range-cross-platform}
	\end{subfigure}
	\hfill % 在第二部分和第三部分之间添加弹性间距
	% 4. 第三部分：只有一张图
	\begin{subfigure}[b]{0.203\textwidth}
		\centering
		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
		\caption{Dig Dataset}
		\label{fig: range big dataset}
	\end{subfigure}

@@

>>>>

		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
		\caption{Hybrid Query Example}

@@

		\caption{Graph Index and IVF Index}

@@

		\caption{\textcolor{orange}{Comparison of AF-ANN and RF-ANN Search Algorithms}}
		\small
%		\label{tab:compair_1}
%		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
%			\hline
%			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
%			\hline
%			NHQ & Graph & C & Y & N& N& N & N & N \\
%			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
%			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
%			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
%			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
%			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
%			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
%			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\
%			
%			\hline
%			
%		\end{tabular}
	\label{tab:compair_1}
	\begin{tabular}{|l|l|*{12}{c|}}
		\hline

@@

			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
			\caption{Construction Time}
			\label{fig:build_time_comparison_query1}
		\end{subfigure}

@@

			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
			\caption{Index Size (Including Original Dataset)}
			\label{fig:index_size_mb_comparison_query1}
		\end{subfigure}

@@

			\includegraphics[width=0.99\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Build Peak Memory }
			\label{fig:build_memory_mb_comparison}
		\end{subfigure}

@@

			\includegraphics[width=0.99\linewidth]{figures/searchMem/label_memory_comparison.pdf}
			\caption{Search Peak Memory}
			\label{fig:search_memory_mb_comparison}
		\end{subfigure}

		%		\caption{Time and space overhead of attribute filtering index construction}
		\caption{\textcolor{violet}{Time and Space Overhead}}
		\label{fig:build_index_comparison}
	\end{figure}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (Single Thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
%		\caption{Single-Attribute Building and Query performance (16 threads)}
		\caption{Performance of Single-Attribute Index Construction and Single-Attribute Query (16 Threads)}
		\label{fig:exp_1_2_SingleLabel_16thread}
	\end{figure*}

@@

	\textit{\textbf{Single-Attribute Index Construction and Single-Attribute Query.}}
	In this scenario, we construct the index using an attribute and apply filtering conditions on the same attribute.

@@

	\textit{\textbf{Multi-Attribute Index Construction and Single-Attribute Query.}}
	In this scenario, the index is constructed using 8 attributes but applies filtering condition on only 1 attribute during the query.

@@

		% 下面的子图，居中显示
		\includegraphics[width=0.7\columnwidth]{figures/exp/exp_2_1.pdf}
		\caption{Effect of Multi-Attribute Index Construction on Single-Attribute Query Performance ($S$ denotes single-attribute index construction and single-attribute query, $M$ denotes multi-attribute index construction and single-attribute query)}
		\label{fig:exp_2_1}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
		\caption{Performance of Multi-Attribute Index Construction and Multi-Attribute Query (single thread)}
		\label{fig:exp_4_1_MultiLabel_1thread}
	\end{figure*}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of Attribute Distribution on Query Performance (Strong is robust to attribute distribution shifts, Weak is sensitive to attribute distribution shifts) (Single Thread) }
		\label{fig:exp_3_1}

%		\footnotesize{
%		\begin{center}
%			\begin{minipage}{\linewidth}
%				\centering	
%				\textit{Strong} : robust to attribute distribution shifts,  \textit{Weak} : sensitive to attribute distribution shifts
%			\end{minipage}
%		\end{center}
%		}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Index Construction and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world scenarios. To evaluate algorithm performance under this setting, we construct the index using 3 uniformly distributed attributes and apply filtering on all 3 attributes simultaneously during queries. \textcolor{violet}{In this experiment, we only evaluate algorithms that support this multi-attribute query scenario.}

@@

			\includegraphics[width=0.95\textwidth]{figures/exp/exp_5_2_1.pdf}
			\caption{Algorithms Optimized for Low AS}
			\label{fig:exp_5_2_1}
		\end{subfigure}

@@

			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_2.pdf}
			\caption{Algorithms Optimized for High AS}
			\label{fig:exp_5_2_2}
		\end{subfigure}
		\hspace{1mm} % 增加水平间距
		\begin{subfigure}{0.33\textwidth} % 1/3 宽度
			\centering

			\includegraphics[width=0.96\textwidth]{figures/exp/exp_5_2_3.pdf}
			\caption{Algorithms Insensitive to AS}
			\label{fig:exp_5_2_3}
		\end{subfigure}

		\caption{Different AS under the Same Algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

	\begin{figure*}
		\centering
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
		\caption{Effect of Different Datasets on AF-ANN Search}
		\label{fig:exp_6_1}
	\end{figure*}

@@

	% 2. 第一部分：两张图，共用标题
	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
	% 宽度从\textwidth缩小到0.32\textwidth
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
		\caption{Multi-Modal}
		\label{fig:attribute-multimodal} 
	\end{subfigure}
	\hfill % 在第一部分和第二部分之间添加弹性间距
	% 3. 第二部分：两张图，共用标题
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
		\caption{Cross-Platform}
		\label{fig:attribute-cross-platform}
	\end{subfigure}
	\hfill % 在第二部分和第三部分之间添加弹性间距
	% 4. 第三部分：只有一张图
	\begin{subfigure}[b]{0.203\textwidth}
		\centering
		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
		\caption{Big Dataset}
		\label{fig:attribute big dataset}
	\end{subfigure}

	% 5. 全局总标题
	\caption{\textcolor{violet}Scalability Study——Attribute}
	\label{fig:TrinityExtension——Attribution_main}
\end{figure*}

@@

	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}} \textcolor{blue}{

@@

		% 三图横排
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\captionsetup{font=small}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{\footnotesize Construction Time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{\footnotesize Index Size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{\footnotesize Build Peak Memory}
			\label{fig:rangeFilter_build_memory_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.495\columnwidth}
			\centering
			\includegraphics[width=\linewidth]{figures/searchMem/range_memory_comparison.pdf}
			\caption{\footnotesize Search Peak Memory}
			\label{fig:rangeFilter_search_memory_mb}
		\end{subfigure}

		%		\caption{Time and space overhead of range filtering index construction}
%		\caption{Time and space overhead of index construction}
		\caption{\textcolor{violet}{Time and Space Overhead}}
		\label{fig:rangeFilter_build_index_comparison}
	\end{figure}
	\subsection{Range Filtering}
	\textcolor{blue}{Due to the limitations of existing range filtering algorithms, our experiment uses only a single attribute, with the dataset sorted in ascending order by value. The WIT-Real and YT-Audio-Real datasets use real attribute values, while the rest use randomly generated ones. }
	\subsubsection{Time and Space overhead of index construction.}

@@

		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
		\caption{Performance of RF-ANN Search}
		\label{fig:exp_8_2}
	\end{figure*}

@@

	\begin{figure*}[htbp]
		\centering
		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Effect of Different Datasets on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

@@

	% 2. 第一部分：两张图，共用标题
	% [b]表示按底部对齐，在一行内通常比顶部对齐[t]效果好
	% 宽度从\textwidth缩小到0.32\textwidth
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
		\caption{Multi-Modal}
		\label{fig:range-multimodal} 
	\end{subfigure}
	\hfill % 在第一部分和第二部分之间添加弹性间距
	% 3. 第二部分：两张图，共用标题
	\begin{subfigure}[b]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
		\caption{Cross-Platform}
		\label{fig:range-cross-platform}
	\end{subfigure}
	\hfill % 在第二部分和第三部分之间添加弹性间距
	% 4. 第三部分：只有一张图
	\begin{subfigure}[b]{0.203\textwidth}
		\centering
		% !!! 注意：这是一个占位符，请替换成您自己的第五张图 !!!
		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
		\caption{Big Dataset}
		\label{fig: range big dataset}
	\end{subfigure}

@@

	\textit{\textbf{\textcolor{blue}{Multi-Modal Queries.}}}
	\textcolor{blue}{
		Similar to attribute filtering, the performance of multimodal queries with range filtering shown in Figure~\ref{fig:range-multimodal} is also consistent with the single-modality results in Figure~\ref{fig:exp_8_2}. As shown in Figure~\ref{fig:exp_8_3}, the algorithms still perform the worst on multimodal datasets like Text2Image. This is because these range query algorithms are almost graph-based. Graph algorithms need more iterations to find true neighbors in OOD datasets.}
